`r glue::glue('inferCNV results for {params$library_id} with {params$reference_name} reference')`

### 2025-05-12 analyses/infercnv-consensus-cell-type/template-notebooks/SCPCP000015_explore-infercnv-results.Rmd
prop_cnv_df fix

```{r}
# First, construct data frame with proportion_scaled_ instead of has_cnv
prop_cnv_df <- infercnv_df |>
  tidyr::pivot_longer(
    starts_with("proportion_scaled_"),
    names_to = "cnv_type_raw",
    values_to = "proportion"
  ) |>
  # more tidying
  dplyr::mutate(cnv_type_raw = stringr::str_remove(cnv_type_raw, "^proportion_scaled_")) |>
  tidyr::separate(cnv_type_raw, sep = "_", into = c("cnv_type", "chr")) |>
  # remove extra chromosomes and cells not in this library
  dplyr::filter(
    !stringr::str_starts(chr, "chrMT"),
    !stringr::str_starts(chr, "chrGL"),
    library_id == params$library_id
  ) |>
  # set chr factor levels, with ones used for validation first
  dplyr::mutate(
    chr = stringr::str_remove(chr, "^chr"),
    chr = factor(chr, levels = 1:22),
    chr = forcats::fct_relevel(chr, as.character(validation_df$chromosome))
  ) |>
  # finally, join in the cell types
  dplyr::inner_join(
    has_cnv_df |>
      dplyr::select(barcodes, celltype)
  )
```

>>>>

```{r}
# First, construct data frame with proportion_scaled_ instead of has_cnv
prop_cnv_df <- infercnv_df |>
  # selecting here is helpful for debugging and viewing results
  dplyr::select(
    starts_with("proportion_scaled_"),
    cell_id,
    library_id,
    barcodes,
    subcluster
  ) |>
  tidyr::pivot_longer(
    starts_with("proportion_scaled_"),
    names_to = "cnv_type_raw",
    values_to = "proportion"
  ) |>
  # more tidying
  dplyr::mutate(cnv_type_raw = stringr::str_remove(cnv_type_raw, "^proportion_scaled_")) |>
  tidyr::separate(cnv_type_raw, sep = "_", into = c("cnv_type", "chr")) |>
  # remove extra chromosomes
  dplyr::filter(
    !stringr::str_starts(chr, "chrMT"),
    !stringr::str_starts(chr, "chrGL")
  ) |>
  # set chr factor levels, with ones used for validation first
  dplyr::mutate(
    chr = stringr::str_remove(chr, "^chr"),
    chr = factor(chr, levels = 1:22),
    chr = forcats::fct_relevel(chr, as.character(validation_df$chromosome))
  ) |>
  # finally, join in the cell types
  dplyr::inner_join(
    has_cnv_df |>
      dplyr::select(barcodes, celltype),
    # we're joining a wide and long df, so we expect many matches
    relationship = "many-to-many"
  )
```
